\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-01 chapters/supplementary.tex
Add dendrograms; finish rewriting experiments sec.

\section{Supplementary material}

@@

\begin{table*}[t]
\centering
    \scriptsize
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{CREMI-Score\\(higher better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
    CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0$. We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments.}
    \label{tab:extended_results_cremi}
\end{table*}

@@

>>>>

\section{Supplementary material}
\TODO{Use S notation for the sections!}

@@

\begin{table*}[t]
\centering
    \scriptsize
        \begin{tabular}{l|c|c|c|c|c}
          \algname{} linkage & \makecell{CREMI-Score\\(lower better)}  & \makecell{Rand-Score\\(higher better)} & \makecell{VI-merge\\(lower better)} & \makecell{VI-split\\(lower better)} & \makecell{Runtime\\(lower better)} \\ \midrule
Average & \textbf{0.226} & \textbf{0.936} & 0.315 & 0.494 & 3.49 $\cdot$ 10$^4$ \\
Sum + CLC \cite{levinkov2017comparative} & 0.282 & 0.906 & 0.358 & 0.510 & 4.64 $\cdot$ 10$^4$ \\
Abs Max \cite{wolf2018mutex} & 0.322 & 0.897 & 0.286 & 0.735 & 1.24 $\cdot$ 10$^4$ \\
Max + CLC & 0.324 & 0.893 & 0.292 & 0.698 & 6.31 $\cdot$ 10$^4$ \\
Sum \cite{keuper2015efficient} & 0.334 & 0.872 & 0.461 & 0.444 & 4.74 $\cdot$ 10$^4$ \\
Average + CLC & 0.563 & 0.772 & 0.259  & 1.142 & 2.95 $\cdot$ 10$^4$ \\
Min & 2.522 & 0.030 & \textbf{0.197} & 6.365 & 2.97 $\cdot$ 10$^3$ \\
Min + CLC & 2.522 & 0.030 & \textbf{0.197}  & 6.365 & 4.77 $\cdot$ 10$^3$ \\
Max & 2.626 & 0.028 & 7.069 & \textbf{0.026} & \textbf{6.04 $\cdot$ 10$^\mathbf{2}$} \\
        \end{tabular}
        \vspace*{1.1em}
    \caption{Performances achieved by different versions of \algname{} on the CREMI 2016 training set. 
    CREMI-Score \cite{cremiChallenge}, is given by a combination of the Adapted Rand-Score (Rand-Score) and the Variation of Information Score for under-clustering (VI-merge) and over-clustering (VI-split) \cite{arganda2015crowdsourcing}.
    CLC stands for cannot-link constraints. For all algorithms, the chosen value of bias parameter was $\beta = 0.5$. We used a machine with CPU Intel(R) Xeon(R) E7-4870 @ 2.40GHz for our comparison experiments. \TODO{Need to include scores Single and Complete linkage!}}
    \label{tab:extended_results_cremi}
\end{table*}

@@

\begin{figure}[t]
\centering
\begin{minipage}[t]{0.48\textwidth}
\vspace{0pt}
\centering
% \footnotesize
\begin{tabular}[t]{L{9em} M{7em}}
           Method & Rand-Score \\ \midrule
           \textbf{GASP Average} & \textbf{0.8966} \\
GASP Sum & 0.8965 \\
GASP Abs Max & 0.8932 \\
SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG} & 0.5839\\
$L_{sym}$ \cite{kunegis2010spectral} & 0.1931 \\
SPONGE \cite{Cucuringu2019SPONGEAG} & 0.0789 \\
BNC \cite{chiang2012scalable} & 0.0074 \\
        \end{tabular}
    \captionof{table}{\algname{} compared to spectral clustering methods on a small crop of the CREMI dataset (sample B).}
    \label{tab:cremi_spectral_experiments}
\end{minipage}
% \begin{minipage}[t]{0.38\textwidth}
% \vspace{0pt}
% \centering
%         \includegraphics[width=1.\textwidth,trim=0.25in 0.25in 0.68in 0.36in,clip]{./figs/SSBM_experiments.pdf} % 0.45
%         \caption{\algname{} performances compared to spectral methods on synthetic graphs. The spectral methods were given the true number of clusters as input, in contrast to \algname{}. \TODO{Define paramters SSB; explain percentile stuff (for both noise experiments, save space!)}}
%     \label{fig:SSBM_scores}
% \end{minipage}
\end{figure}

\section{Comparison with spectral clustering} \label{sec:spectral_clust}
In this section we compare \algname{} to spectral clustering (SC) methods for signed graphs both on synthetic graphs and real ones from neuron segmentation. These methods require the user to specify the number of clusters in advance, in contrast to our proposed agglomeration method that determines the cluster number based on the signed weights of the graph. In the following comparison, we make these baselines as strong as possible by specifying the true number of clusters for the spectral methods.

\textbf{Synthetic graphs} -- First, we compare the clustering performance on synthetic graphs generated by a signed stochastic block model (SSBM), where SC performs well. In particular, we used an Erd\H os-R\'enyi random graph model $\mathcal{G}(N,p)$ with $N=10^5$ vertices and edge probability $p=0.1$. Following the approach in \cite{Cucuringu2019SPONGEAG}, we partitioned the graph into $k=100$ equally-sized clusters, such that edges connecting vertices belonging to the same cluster (different clusters, respectively) had Gaussian distributed edge weights centered at $\mu=1$ ($\mu=-1$, respectively) and with standard deviation $0.1$. To model noise, we flipped the sign of each edge independently with probability $\eta \in [0, 0.4]$. Median scores, 25th and 75th percentiles over 30 repetitions are shown in Fig.~\ref{fig:SSBM_spectral_experiments}: GASP achieved scores comparable to SPONGE$_{sym}$ \cite{Cucuringu2019SPONGEAG}, a recently proposed SC method. The specific design choice of a \emph{sign flipping} noise used in the SSBM experiments turned out to favor GASP with \emph{Sum} linkage that, according to the experiments presented in Sec.~\ref{sec:results}, is the one with the lowest tendency to over-cluster and grows one cluster at the time.

\textbf{Neuron segmentation} -- We extended the comparison with spectral methods to the task of neuron segmentation. Since SC cannot scale to the full CREMI dataset, we evaluated \algname{} and SC on a smaller $10\times100\times100$ voxels volume resulting in a graph with $10^5$ nodes and~$\sim10^6$ edges. Scores are summarized in Table \ref{tab:cremi_spectral_experiments}.
%suggested by the reviewer that performed best in the recent comparison \cite{Cucuringu2019SPONGEAG}: one based on the Balanced Normalized Cut (BNC) \cite{chiang2012scalable}; another on the symmetrically normalized Signed Laplacian ($L_{sym}$) \cite{kunegis2010spectral}; SPONGE and SPONGE$_{sym}$ algorithms were recently proposed in \cite{Cucuringu2019SPONGEAG}.
Despite the fact that the true number of ground truth clusters was given as an input to the SC methods, GASP significantly outperformed them on neuro-data. SC methods seem to have more difficulties when the graph is sparse. Moreover, they did not handle well pixels on the boundaries between segments and tended to cluster them together. Increasing $k$ did not improve their scores either.

\begin{prop}\label{prop:MWS_SSBM_1}
Consider a graph $\mathcal{G}(V,E)$ generated with a SSBM with parameters $N,p,k,\sigma$ and an associated ground truth (GT) clustering $\hat{\Pi}=\{\hat{S}_1, \ldots, \hat{S}_k\}$. Then, assume that after some merging-iterations of the MWS algorithm the clustering $\Pi$ is found. Then, any two clusters $S_i,S_j\in \Pi$ have probability $|E_{ij}| / |E_{\Pi}^1|$ to be selected in the next iteration of the algorithm, where $E_{\Pi}^1$ is the multicut associated to $\Pi$ and $E_{ij}\equiv(S_i\times S_j)\cap E$ is the set of edges connecting the two clusters. 
\end{prop}

\begin{prop}\label{prop:MWS_SSBM_2}
Given the assumptions of Prop.~\ref{prop:MWS_SSBM_1}, let $E_{ij}^+=\{(u,v) \in E_{ij} | \exists \hat{S}\in \hat{\Pi} \, \mathrm{s.t.} \, u\in \hat{S} \wedge v\in \hat{S} \}$ denote the set of true attractive GT edges connecting two clusters $S_i,S_j$
\begin{equation}
\sum_{ij} \frac{|E_ij^+|}{||}
\end{equation}
\end{prop}

Then, the MWS algorithm will assign highest priority to 
Among these edges, we define the set of true attractive GT edges as . Finally, let $f^+=|E_{ij}^+| / |E_{ij}|$ denote the fraction of true attractive edges. Then, the Mutex Watershed algorithm

\begin{itemize}
\item each pair of clusters $S_i,S_j$ has probability $|E_{ij}| / |E_{\Pi}^1|$ to have the interaction with highest priority 
\item if the pair of clusters $S_i,S_j$ is given the highest priority by the MWS Algorithm, then they have has a probability $p^+=f^+(1-\eta) + f^+ \eta$ to be merged and $p^-=1-p^+$ to be constrained.
\end{itemize}
will assign a positive interaction to clusters $S_i,S_j$ with probability $f^+(1-\eta) + f^+ \eta$. 
Remarks: this quantity does not depend on the size of $|E_{ij}|$ (so it won't change when clusters grow in size); if $f^+=1$ (i.e. $S_i,S_j$ are subclusters of the same GT cluster), then MWS will merge them with probability $1-\eta$; if $f^+=0$ (i.e. $S_i,S_j$ are subclusters of two different GT clusters), then MWS will merge them with probability $\eta$.
\TODO{Assumption about $\sigma$?}
